pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-01-21 article.tex
Progress

>>>>

The goal of \verb;pirouette; is to measure the inference error BEAST2
makes from a given/known/true phylogeny. This involves multiple steps,
described in detail below. 
In brief: from a given phylogeny, an alignment is simulated, from which a BEAST2
posterior is inferred, of which its phylogenies are compared with the given
phylogeny. The more the posterior phylogenies match the given phylogeny,
the lower the error. The is also the option to generate a 'twin tree',
that goes through the same pipeline.

The first step simulates a DNA alignment from the given phylogeny.
One can specify a DNA sequence
of any length at the root of the phylogeny, a DNA mutation rate, a
site (also: nucleotide substitution) model, 
a clock model, a random number generator (RNG) seed and a location
where the alignment is saved to. This step is relatively fast, but longer
DNA alignments will noticably slow down the inference step.

The second step selects an inference model, using the alignment.
The user can specify to use the generative model or select a best model
from a set of inference models. When selecting the generative model,
the site and clock model used in the alignment simulation are used
in inference. Because the given phylogeny (on which the alignment is based)
may have followed any tree prior (also: speciation model), the user needs
to specify which tree prior is used in inference. When selecting a best
model, the alignment is used to find the inference model that has the
highest evidence (also: marginal likelihood)

The third step infers a Bayesian posterior from the simulated alignment.
From the
DNA alignment a Bayesian posterior is generated, using a user-specified
inference setup. The given tree is compared with all posterior trees, using
a user-specified error measurement setup.

A first and optional step is to generate a 'twin tree', that will be
analyzed in the same way as the true tree.
